Appendix A: Deep Reinforcement Learning

### 2021-06-09 appendices/appendix-A-definitions.Rmd
Ooops forgot to add appendix A

output: 
  rticles::arxiv_article:
    keep_tex: true
    extra_dependencies:
      algorithm: null
      algpseudocode: noend

@@

Policy gradients, value-based and actor-critic methods are the general classes of algorithms for gradient-based model-free RL.
In this section, we will go over these algorithm classes to convey a sense of what they are attempting to achieve and the trade-offs between them.

>>>>

output: 
  rticles::arxiv_article:
    extra_dependencies:
      algorithm: null
      algpseudocode: noend

@@

To solve the RL problem, algorithms either take a *model-free* or *model-based* approach. 
The distinction is that *model-free* algorithms do not attempt to learn or use a model of the environment; yet, *model-based* algorithms employ a model of the environment to achieve the RL objective.
A trade-off between these approaches is that when it is possible to quickly learn a model of the environment or the model is already known, model-based algorithms tend to require much less interaction with the environment to learn good-performing policies [@mbpo].
Yet, frequently, learning a model of the environment is very difficult, and in these cases, model-free algorithms tend to outperform [@mbpo].
Since our examples use model-free agents, we will focus on model-free algorithms in this section.

Among model-free methods, there is divergence around what functions the agent is attempting to learn in order to achieve the RL objective.
Generally, model-free agents are either learning a policy function, a value function or both.
For context, *value functions* are proxies for how high of a cumulative reward an agent can expect to receive from a given state or state-action pair.
If an agent knows the value function, then the agent can find the optimal action at any state by selecting the action that will maximize the value function in expectation.
The class of algorithms that exclusively try to learn a value function are called *value-based* methods.
In contrast, *policy gradient* algorithms exclusively learn the policy.
And, lastly, *actor-critic* algorithms attempt to learn both a policy and value function, whereby the value function is used to inform the agent on the goodness of a selected action.
We will go into further detail on these different approaches below.
